---
title: "p8105_hw6_stl2137"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
set.seed(1)
```

# Problem 1

```{r}
birthweight_data <- read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )
```

I chose the following variables to build a model that predicts baby birth weight based off prior knowledge of what variables are associated with birthweight: `babysex` or the gender, `bhead` or the baby’s head circumference at birth in centimeters, `blength` or the baby’s length at birth in centimeters, `gaweeks` or the gestational age in weeks, `malform` or presence of malformations that could affect weight, and `smoken` or average number of cigarettes smoked per day during pregnancy.

```{r}
birthweight_model <- lm(bwt ~ babysex + bhead + blength + gaweeks + malform + smoken, data = birthweight_data)

birthweight_data %>% 
  modelr::add_predictions(birthweight_model) %>% 
  modelr::add_residuals(birthweight_model) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point()
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
main_effects_model <- lm(bwt ~ blength + gaweeks, data = birthweight_data)

interactions_model <- lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead *babysex + blength*babysex + bhead*blength*babysex, data = birthweight_data)
```

```{r}
cv_df = 
  crossv_mc(birthweight_data, 4342) 

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df <- 
  cv_df %>% 
  mutate(birthweight_train_mod = map(train, ~lm(bwt ~ babysex + bhead + blength + gaweeks + malform + smoken, data = .x)), 
         main_effects_train_mod = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         interaction_train_mod = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead *babysex + blength*babysex + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_birthweight = map2_dbl(birthweight_train_mod, test, ~rmse(model = .x, data = .y)),
    rmse_main_effects = map2_dbl(main_effects_train_mod, test, ~rmse(model = .x, data = .y)),
    rmse_interaction = map2_dbl(interaction_train_mod, test, ~rmse(model = .x, data = .y))
  )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
simple_temp_model <- lm(tmax ~ tmin, data = weather_df) 

simple_temp_model %>% 
  broom::glance()
```

