---
title: "p8105_hw6_stl2137"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# Problem 1

```{r}
birthweight_data <- read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )
```

Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}
birthweight_model <- lm(bwt ~ babysex + bhead + blength + gaweeks + malform + smoken, data = birthweight_data)

birthweight_data %>% 
  modelr::add_predictions(birthweight_model) %>% 
  modelr::add_residuals(birthweight_model) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point()
```

Compare your model to two others:

* One using length at birth and gestational age as predictors (main effects only)

* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
main_effects_model <- lm(bwt ~ blength + gaweeks, data = birthweight_data)

interactions_model <- lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead *babysex + blength*babysex + bhead*blength*babysex, data = birthweight_data)
```

# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

